### 2018-10-08 Sections/protocols_for_the_quantum_internet.tex
Stub W-state memory
W state memory

>>>>

%
% Error correction
%

\subsection{Error correction}\index{Quantum error correction}

Since quantum memories are subject to errors that accumulate with time, long-life quantum memories will necessarily require error correction mechanisms to preserve qubit states held within them.

To achieve this, standard QEC codes (Sec.~\ref{sec:QOS}) can be employed to encode a number of logical qubits into a larger number of physical qubits, which are held in quantum memory and undergo active error correction. Any of the previously discussed QEC techniques are applicable to this.

An alternate approach is to use W-state encoding\index{W-state encoding} to implement unitary error averaging (Sec.~\ref{sec:error_averaging})\index{Unitary error averaging}, where the unitaries are single-qubit channels \cite{errorfilteringpaper, bib:MadhavPeterLund}. The protocol is shown in Fig.~\ref{fig:W_state_memory}. We begin by using a QFT fanout\index{Fanout} operation to encode a dual-rail encoded qubit\index{Dual-rail encoding} across $N$ optical modes. Each optical mode then feeds into a solid-state qubit (e.g a two-level atom), which ideally implement an identity channel but are inevitably subject to usual error processes such as dephasing and amplitude damping (characterised by $T_1$ and $T_2$ times). Finally, the inverse fanout operation is applied and success of the protocol is defined as there being exactly one photon between the first two (`success') output modes. If a photon is detected in any of the other (`failure') modes the state is presumed erroneous and discarded.

\begin{figure}[!htpb]
	\includegraphics[width=0.475\textwidth]{W_state_memory}
	\caption{Quantum memory based on W-state encoding. Rails represent optical modes, and the input logical qubit state, $\ket{L}$, is represented using dual-rail encoding. The QFT fanout operation maps each of the two input basis states to one of two orthogonal $N$-qubit W-states, $\ket{W}$, differing only by their phase relationships. These are then fed into a bank of $N$ quantum memories. To readout the memories we convert back to optical encoding and decode using the inverse QFT operation. Success of the protocol is defined as there being exactly one photon between the first two `success' output modes. If a photon leaks into any of the other `failure' output modes we discard the state and assume it was erroneous. Thus error detection is heralded via the presence or absence of a photon in the `failure' modes.}\label{fig:W_state_memory}
\end{figure}

\comment{Show mathematical results}
